Scattering from compact objects: Regge poles \\ and the Complex Angular Momentum method

### 2019-11-25 rainbowCAM.tex
Numerical method for PR

>>>>

In order to determine the Regge poles we use the method described in sec.~4 of ref.~\cite{Benhar:1998au}. In fact, they had adapted the \textit{continued fraction method}, developed by Leaver in the case of BH-QNM frequencies~\cite{Leaver:1985ax}, to determine the axial QNM frequencies of a compact bodies. Though they used their method to find the QNM frequencies, their method is equally valid, \textit{mutatis mutandis}, for finding the Regge poles. We have implemented numerically this method by using the Hill determinant approach of Majumdar and Panchapakesan~\cite{mp}, or more precisely, by modifying their method and adapting it to our problem, \textit{i.e.}, using it for a 4-term recurrence relation.
